\textbf{\glsfmtfull{ris}:\\Beamforming, Modulation, and Channel Shaping}

### 2024-05-01 viva/slides.tex
:ambulance: Compression

	\begin{frame}{Use case: Beamforming}
		% \textcolor{blue}{Joint beamforming} design of \gls{ris} and transceiver for a specific performance measure \cite{Wu2020}.
		% \gls{ris} and transceiver \textcolor{blue}{joint beamforming} design for a specific performance measure \cite{Wu2020}.
		\textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure \cite{Wu2020}.
		\begin{figure}
			\centering
			\subfloat[Coverage extension]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_coverage.pdf}
				}
			}
			\subfloat[Security enhancement]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_security.pdf}
				}
			}
			\subfloat[Interference mitigation]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_interference.pdf}
				}
			}
			\\
			\subfloat[Assist \glsfmtshort{d2d} network]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_network.pdf}
				}
			}
			\subfloat[Assist information and power transfer]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_swipt.pdf}
				}
			}
		\end{figure}
	\end{frame}

>>>>

	\begin{frame}{Use case: Beamforming}
		% \textcolor{blue}{Joint beamforming} design of \gls{ris} and transceiver for a specific performance measure \cite{Wu2020}.
		% \gls{ris} and transceiver \textcolor{blue}{joint beamforming} design for a specific performance measure \cite{Wu2020}.
		\textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure \cite{Wu2020}.
		\begin{figure}
			\centering
			\subfloat[Coverage extension]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_coverage.jpg}
				}
			}
			\subfloat[Security enhancement]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_security.jpg}
				}
			}
			\subfloat[Interference mitigation]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_interference.jpg}
				}
			}
			\\
			\subfloat[Assist \glsfmtshort{d2d} network]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_network.jpg}
				}
			}
			\subfloat[Assist information and power transfer]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_swipt.jpg}
				}
			}
		\end{figure}
	\end{frame}
